### 2025-11-02 src/articles/article5.qmd
Fix typos and formatting across the repo, Closes #5 (#6)
* fix ibl typo in article 3

* fix cwru typo article 8

* remove redundant backslashes

* fix appendix references

* fix labeling
update in accordance with https://docs.google.com/document/d/16Bhp1ZhyKaanmR8jaZSP-depL2DxAZ5dGMxIQ4VR0w4 (#7)

1. Vice President
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix as outlined in @sec-art-Q8OV40FK.
   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in @sec-art-C89656BJ.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in @sec-art-YOSPIQLS.
   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in @sec-art-VI2T9PVL, Item 3a. o. Must live in the house.

@@

1. Secretary
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in @sec-art-BUK07FVL.
   a. Serves as Secretary of {{< var acronyms.ec >}}.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.
   a. Fills out Greek Life and International Headquarters (IHQ) awards that are due in their term.
   a. Releases a weekly TWIOX (This Week in Theta Chi) newsletter to the alumni mailing list

@@

1. Philanthropy and Service Chair
   a. Serves as chair of the Philanthropy and Service Committee.
   a. Ensures the chapter meets the Greek Life goals for service and philanthropy.
   a. Informs the chapter of service and philanthropy opportunities.
   a. Serves as a member of {{< var acronyms.ccc >}}.

@@

1. The chapter will have the following groups of committees:
   a. Standard Committees
      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
         1. Alumni Relations Committee and Member Development Committee
         1. Health and Safety Committee and Scholarship Committee
         1. Philanthropy and Service Committee and Social Committee
         1. Public Relations Committee and Recruitment Committee
      i. All Standard committees will do the following:
         1. Meet at least once every two weeks as directed by their chair.
            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1. Assist the chair in the discharge of their duties.
         1. Create a set of goals for the committee at the first meeting of the committee.
         1. Work toward the goals of the committee.
   b. Operational Committees
      i. Ad hoc committees
         1. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1. Purpose and Duties
            a. To create a budget for the chapter for the next year pursuant to @sec-art-GD7C1K2U.
            a. To examine any financial issues of the chapter.
         1. Membership
            a. The Treasurer will serve as chair of the Budget Committee.
            a. The body of the committee will be selected by the Treasurer.
         1. Procedure
            a. The committee will be created and convened during the budgeting process outlined in @sec-art-GD7C1K2U, Item 3.
            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
      i. Committee Chair Committee ({{< var acronyms.ccc >}})
         1. Purpose
            a. To facilitate communication between committee chairs.
            a. To keep the Vice President informed of committee business.
            a. To help the Vice President ensure that committees are performing all necessary duties.
         1. Membership
            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
            a. The chairs of all Standard Committees will be members.
            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
         1. Procedure
            a. The committee will meet at least once every two weeks while school is in session.
            a. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1. The Mandatory Bylaw Revision Committee will function in accordance with @sec-art-YOSPIQLS.

>>>>

1. Vice President
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix (@sec-art-LGUUVLYZ) as outlined in @sec-art-Q8OV40FK.
   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in @sec-art-C89656BJ.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in @sec-art-YOSPIQLS.
   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in @sec-art-VI2T9PVL, Item 3a. o. Must live in the house.

@@

1. Secretary
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in @sec-art-BUK07FVL.
   a. Serves as Secretary of {{< var acronyms.ec >}}.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Releases a weekly TWIOX (This Week in Theta Chi) newsletter to the alumni mailing list

@@

1. Philanthropy Chair
   a. Serves as chair of the Philanthropy Committee.
   a. Ensures the chapter meets the Greek Life goals for philanthropy.
   a. Informs the chapter of philanthropy opportunities.
   a. Responsible for planning and holding one philanthropy event per semester.
   a. Responsible for having one philanthropy event per academic year benefit the USO.
   a. Serves as a member of {{< var acronyms.ccc >}}.

1. Service Chair
   a. Serves as chair of the Service Committee.
   a. Ensures the chapter meets the Greek Life goals for service.
   a. Informs the chapter of service opportunities.
   a. Responsible for planning and holding at least one service event for the chapter per semester.
   a. Responsible for tracking the service hours of active brothers.
   a. Serves as a member of {{< var acronyms.ccc >}}.

@@

1. The chapter will have the following groups of committees:
   a. Standard Committees

      i. The list of Standard committees is as follows:
         1. Alumni Relations Committee
         1. Member Development Committee
         1. Health and Safety Committee
         1. Scholarship Committee
         1. Philanthropy Committee
         1. Service Committee
         1. Social Committee
         1. Public Relations Committee
         1. Recruitment Committee
      i. All Standard committees will do the following:
         1. Meet at least once every two weeks as directed by their chair.
            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1. Assist the chair in the discharge of their duties.
         1. Create a set of goals for the committee at the first meeting of the committee.
         1. Work toward the goals of the committee.
   b. Operational Committees
      i. Ad hoc committees
         1. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1. Purpose and Duties
            a. To create a budget for the chapter for the next year pursuant to @sec-art-GD7C1K2U.
            a. To examine any financial issues of the chapter.
         1. Membership
            a. The Treasurer will serve as chair of the Budget Committee.
            a. The body of the committee will be selected by the Treasurer.
         1. Procedure
            a. The committee will be created and convened during the budgeting process outlined in @sec-art-GD7C1K2U, Item 3.
            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
      i. Committee Chair Committee ({{< var acronyms.ccc >}})
         1. Purpose
            a. To facilitate communication between committee chairs.
            a. To keep the Vice President informed of committee business.
            a. To help the Vice President ensure that committees are performing all necessary duties.
         1. Membership
            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
            a. The chairs of all Standard Committees will be members.
            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
         1. Procedure
            a. The committee will meet at least once every two weeks while school is in session.
            a. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1. The Mandatory Bylaw Revision Committee will function in accordance with @sec-art-YOSPIQLS.
